Active Learning from Blackbox to Timed Connectors

### 2016-01-11 paper/paper.tex
.

% style of source code environment listings
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{framextopmargin=50pt,frame=bottomline, language=Golang}

@@

As shown in Figure \ref{fig:reoconnector}, we use a simple example to illustrate how complex
connectors are constructed and used in coordination. In this example, COM1,COM2 and
MONITOR are components. With an \emph{alternator} connector, MONITOR can receive data items from
COM1 and COM2 alternately.

@@

As far as we can see, various forms of Mealy machines are defined in different works. In this paper,
we give the formal definition of Mealy machine following \cite{DBLP:conf/sfm/SteffenHM11}.

\todo{why we choose this version}

@@

\subsection{Active Learning}

@@

\section{From Blackbox to Timed Connectors}

@@

\subsection{An Example of the Reo Package}
As mentioned above, our implementation in \texttt{Golang} is well-prepared not only for academic use
but also for practical concurrent programming.

\begin{lstlisting}
int main(int argc, char ** argv)
{
  printf(``Hello world!n'');
  return 0;
}
\end{lstlisting}

>>>>

% style of source code environment listings
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true, frame=shadowbox}
\lstset{numbers=left}
\lstset{xleftmargin=2em, xrightmargin=2em}
\lstset{language=Golang}

@@

As shown in Figure \ref{fig:reoconnector}, we use a simple example to illustrate how complex
connectors are constructed and used in coordination. In this example, COM1,COM2 and
MONITOR are components. With an \emph{alternator} connector, MONITOR can receive data items from
COM1 and COM2 alternately. The \emph{alternator} example has been implemented in \texttt{Golang} as
shown in Section \ref{sec:reolib}.

@@

As far as we can see, various forms of Mealy machines are defined in different works, wherein some
are deterministic and some are not. Since active automata learning very much depends on the system
under learning to be deterministic, in this paper we formally define a deterministic version of
Mealy machine following \cite{DBLP:conf/sfm/SteffenHM11}.

@@

\subsection{Active Learning}
In this section, we briefly introduce the main ideas of active automata learning.

Active learning \cite{settles2010active} is a special case of semi-supervised machine learning where
a learning algorithm is able to interactively query the target systems to obtain the desired outputs
on certain inputs. With such flexibility, active learning makes it able to use targeted and efficient
queries to obtain more accurate models with smaller dataset.

\todo{a figure illustrating the framework of active learning}

Figure shows a sketch of active learning, wherein
\begin{itemize}
  \item[-]
\end{itemize}

More details on the algorithm will be presented in Section \ref{sec:activelearning}.

@@

\section{From Blackbox to Timed Connectors} 
\label{sec:activelearning}

@@

\subsection{An Example of the Reo Package }
\label{sec:reolib}

As mentioned above, our implementation in \texttt{Golang} is well-prepared not only for academic use
but also for practical concurrent programming. The following code shows how to compose an alternator
connector (see Figure \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example can be found in our github repo.

\begin{lstlisting}
package main

import . './lib/reo'

func alternator(A, B, C Port) {
  // definition of ports
  M0 := MakePort()
  // M1 ... M5 defined similarly

  // definition of channels
  /* NOTE
  go function() means that the function would
  be executed as a new parallel task
  */
  go ReplicatorChannel(A, M0, M1)
  go ReplicatorChannel(B, M2, M3)
  go MergerChannel(M4, M5, C)

  go SyncdrainChannel(M1, M2)
  go SyncChannel(M0, M4)
  go FifoChannel(M3, M5)
}
\end{lstlisting}

Provided with the source and sink nodes, \emph{alternator} function creates a series of basic
channels and mixed nodes (named \emph{Port}) to serve as the alternator connector we need. Now we
can activate the components and using \emph{alternator} function to coordinate them.

\begin{lstlisting}
A := MakePort()
B := MakePort()
C := MakePort()
alternator(A, B, C)

go sender(A, "MSG A")
go sender(B, "MSG B")
go monitor(C)
\end{lstlisting}

In this case, \emph{sender} are goroutines (basic parallel units in \texttt{Golang}) that keep
sending certain messages to some given port (A and B). A \emph{monitor} keep trying to read data
items from the sink end C and print them on the screen. Finally we have a interleaved sequence of
``MSG\_A'' and ``MSG\_B''.
